\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage{titling}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\setlength{\droptitle}{-10em}   % This is your set screw (https://tex.stackexchange.com/questions/29593/shift-title-and-author-text-up) 

\usepackage{indentfirst} % Make identation of first paragraphs

\usepackage[margin=1.6in]{geometry}

\title{Project Proposal}
\date{October 16, 2018}
\author{Machine Learning I \\ \\ 
Aaron A. Gauthier and Pedro Uria Rodriguez}

\begin{document}

\maketitle

\subsection*{Project Title}

\textit{Classification of Mushrooms from the Agaricus and Lepiota Family}.

\subsection*{Problem Definition}

Various guides clearly state that there is no simple rule for determining the edibility of a mushroom. Using data on different features of mushrooms and classification algorithms, we plan to train a model with a high degree of confidence in order to distinguish between edible and poisonous mushrooms for two particular families (namely Agaricus and Lepiota Family). 

\subsection*{Motivation}

We realized that many people in the USA do not know the difference between an edible mushroom and a poisonous one. We hope that through this project we can help educate people on the top significant features that determine whether a mushroom is safe for ingestion or not. We hope this will help save lives and avoid tragedy, especially with children who are curious.

\subsection*{Method}

Data Preprocessing $\longrightarrow$ Model Learning $\longrightarrow$ Model Testing, Understanding and Refining $\longrightarrow$ Comparison between different models $\longrightarrow$ Finding common poisonous traits. \\

The models will include, but are not be limited to: Logistic Regression, Random Forests, K-Nearest Neighbors and Naive Bayes, all of which are present in the \textit{scikit-learn} package for \textit{Python}. We will be using this library, along with \textit{pandas}, \textit{numpy}, \textit{seaborn}, \textit{matplotlib} and other potential ones. We will write our code on Jupyter Notebooks, and use Skype, Slack, GitHub, Dropbox, email and in-person consultations.

\subsection*{Link to the Data}

UCI Machine Learning Repository: \url{https://archive.ics.uci.edu/ml/datasets/mushroom} \\

Mushroom Data and MetaData: \sloppy\url{https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom}

\subsection*{Responsibility of Team Members}

Duties of each team member will include coding, review of coding, strategy, execution, and write-ups. Duties of each team member are a shared responsibility in all facets of the project. 


\end{document}